---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Hydrosystems
===============

R functions for hydrological modeling and water resources systems analysis.

## Overview
===============

Currently version of the package includes functions for:

+ Financial analysis (Net Present Value) 
+ Potential evapotranspiration calculation by Hamon and Hargreaves equations
+ Hydrological simulation using abcd and abcde models
+ Rule-based reservoir operations simulation 
+ Optimization using Shuffled Complex Evolution algorithm
+ Various helpers for data munging & visualization

## Installation
===============

install directly from github using the devtools package. First install devtools,
instructions can be found here: https://github.com/hadley/devtools

```{r, echo = FALSE}
devtools::install_github('tanerumit/hydrosystems')
```


## Getting started
===============

```{r}
library(hydrosystems)
```

